Races with hyper3 objects

### 2022-05-22 inst/race3.Rmd
more work and algebra

With four competitors we have five nontrivial order statistics which,
without loss of generality, are $(a,b,a,a)$ and $(a,a,b,a)$.
$(a,b,a,b)$, $(a,b,b,a)$, $(a,b,c,a)$. Taking $(a,b,a,b)$ as an
example we have

$$
\mathcal{L}(a)=
\frac{a}{2a+2b}\cdot
\frac{b}{ a+2b}\cdot
\frac{a}{ a+ b}\cdot
\frac{b}{    b}=\frac{a^2-a^3}{4-2a}
$$

@@

If we allow non-finishers there is another nontrivial order statistic,
viz $\left(a,b,\left\lbrace a,b\right\rbrace\right)$:

@@

>>>>

With four competitors we have five nontrivial order statistics which,
without loss of generality, are:

* $a\succ b\succ a\succ a$
* $a\succ a\succ b\succ a$
* $a\succ b\succ a\succ b$
* $a\succ b\succ b\succ a$
* $a\succ b\succ c\succ a$.

Taking $a\succ b\succ a\succ b$ as an example we have

$$
\mathcal{L}_{a\succ b\succ a\succ b}(a)=
\frac{a}{2a+2b}\cdot
\frac{b}{ a+2b}\cdot
\frac{a}{ a+ b}\cdot
\frac{b}{    b}=\frac{a^2-a^3}{4-2a}
$$

@@

If we allow non-finishers there is another nontrivial order statistic,
viz $a\succ b\succ\left\lbrace a,b\right\rbrace$ [thus one of the two
$a$'s won, one of the $b$'s came second, and one of each of $a$ and
$b$ failed to finish].

@@

```{r}
fisher <- function(a){(1+16*a+18*a^2-4*a^3-15*a^4-7*a^5-a^6)/(a*(1-a)*(1+a)^3)}
a <- seq(from=0.05,to=0.95,by=0.01)
plot(a,fisher(a))
```
